Clustering time series based on probability distributions across temporal granularities

### 2021-11-07 main.Rmd
S2 and S3 plots caption and title revised

```{r gran2and1-clubbed, fig.cap=" Plots (b) and (c) correspond to Scenarios (b) and (c) respectively. In (b) $g2$, $g3$ changes across atleast one design but $g1$ remains constant. Only $g3$ changes across different designs in (c)."}
#gran2_change  + gran1_change + plot_layout(widths = c(1,1))
#ggpubr::ggarrange(gran1_change, gran2_change, labels = c("a", "b"))
```

>>>>

```{r gran2and1-clubbed, fig.cap=" Boxplots showing distributions of categories across different designs (rows) and granularities (columns) for scenarios S2 and S3. In S2, $g2$, $g3$ change across atleast one design but $g1$ remains constant. Only $g3$ changes across different designs in S3."}
#gran2_change  + gran1_change + plot_layout(widths = c(1,1))
#ggpubr::ggarrange(gran1_change, gran2_change, labels = c("a", "b"))
```
